Computer Science House Constitution

### 2016-02-15 articles.tex

\asection{Maintainers}

\asubsection{Maintainer Qualifications}
Maintainers must have Active or Alumni in good standing status.

\asubsection{Maintainer Expectations}
Maintainers are expected to:
\begin{itemize}
    \item Review changes to the Constitution for grammar, spelling, and internal consistency.
    \item Participate in discussion of proposals.
    \item Facilitate the creation of new changes to the Constitution by other members.
    \item Be knowledgeable about the Constitution. 
\end{itemize}
Failure to adequately meet any of these expectations is grounds for revocation of maintainer status.

\asubsection{Maintainer Resignations}
Maintainers may resign at any time by notifying the current eboard and maintainer group.

\asubsection{Maintainer Term}
Maintainer status lasts until it is resigned, or revoked by Executive Board vote.

\asubsection{Maintainer Selection}
Any member may nominate a qualified member for Maintainer status to the Executive Board for consideration. The Exective Board may choose to approve or reject the nomination by Simple Majority vote.

@@

\asection{Qualifications}
\asubsection{Qualifications to be the Chairman, Evaluations Director}
\begin{enumerate}
	\item Candidates must be Active Members during the term of office.
	\item Candidates must reside on floor during the term of office.
	\item Candidates must have at least one full semester of House membership as an Active Member.
	\item Elected or selected candidates may not hold two simultaneous voting Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position.
\end{enumerate}
\asubsection{Qualifications to be the Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director}
\begin{enumerate}
	\item Candidates must be Active Members during the term of office.
	\item Candidates must have at least one full semester of House membership as an Active Member.
	\item Elected or selected candidates may not hold two simultaneous voting Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position.
\end{enumerate}
\asubsection{Qualifications to be the Operational Communications Director}
\begin{enumerate}
	\item Candidates must be a current Root Type Person \ref{Operations of the Operational Communications Directorship}
	\item Candidates must be a current Active Member.
	\item A Root Type Person cannot be the director if they currently hold any other Executive Board Position.
\end{enumerate}

>>>>

@@

\asection{Qualifications}
\asubsection{Qualifications to be the Chairman, Evaluations Director, Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director}
\begin{enumerate}
	\item Candidates must be Active Members during the term of office.
	\item Candidates must have at least one full semester of House membership as an Active Member.
	\item Elected or selected candidates may not hold two simultaneous voting Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position.
\end{enumerate}
\asubsection{Qualifications to be the Operational Communications Director}
\begin{enumerate}
	\item Candidates must be a current Root Type Person \ref{Operations of the Operational Communications Directorship}
	\item Candidates must be a current Active Member.
	\item A Root Type Person cannot be the director if they currently hold any other Executive Board Position.
\end{enumerate}
